In Depth Analysis of Event Patterns in Crisis Situations

### 2024-01-22 outputs/paper/paper.qmd
work sunday

### Neighbourhood and Suicide PIC Calls ###
@fig-hood shows the relationship between neignbourhood and suicide PIC calls. There are around 174 neighbourhoods divided in Hood_158 system and the graph shows around 158 neighbourhoods have reported a PIC call for suicide-related events. The most number of calls were received from Hood 170 which were about 1022 suicide related calls and second most calls from recieved from the area Hood_73 which were around 858 calls. The Hood_170 is Yonge-Bay
Corridor area and Hood_73 is Moss Park area in Old City of Toronto.(Toronto neigbourhoods #https://www.toronto.ca/city-government/data-research-maps/neighbourhoods-communities/neighbourhood-profiles/about-toronto-neighbourhoods/)

### Suicides and Apprehension made ###

```{r}
#| label: fig-planes2
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)
library(patchwork)
day_colors <- c("Sunday" = "red", "Monday" = "green", "Tuesday" = "blue", "Wednesday" = "purple",
                "Thursday" = "orange", "Friday" = "brown", "Saturday" = "pink")
# Create ggplot objects for days and time
days <- cleaned_data %>%
  ggplot(aes(x = fct_infreq(event_dow), fill = fct_infreq(event_dow))) +
  geom_bar(position = "stack", show.legend = FALSE) +
  labs(x = "Day of Week", y = "Frequency", fill = "Day of Week") +
  scale_fill_manual(values = day_colors) +
  theme_minimal()

time <- cleaned_data %>%
  mutate(Time=as.POSIXct(event_hour, format="%H")) %>%
  ggplot(aes(Time, fill=fct_infreq(event_dow))) +
  geom_density(adjust=0.5, position="stack") + # Stack the KDE of each day on top of each other
  labs(x = "Time of Day", y = "Density", fill="Day of Week") +
  scale_x_datetime(date_labels="%H", breaks="4 hour") +
  scale_fill_manual(values=day_colors) +
  theme(legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(-5,-5,-5,-5),
        axis.text.x=element_text(size=8)) +
  ggtitle("Delays Spike Several Times Throughout the Day")

# Plot the two graphs on top of each other with a space in between
(days / plot_spacer() / time +
    plot_layout(heights = c(10, 1, 6), guides="collect"))

>>>>

### Neighbourhood and Suicide PIC Calls ###
@fig-hood shows the relationship between neighborhood and suicide PIC calls. There are around 174 neighborhoods divided in Hood_158 system and the graph shows around 158 neighborhoods have reported a PIC call for suicide-related events. The most number of calls were received from Hood 170 which were about 1022 suicide related calls and second most calls from received from the area Hood_73 which were around 858 calls. The Hood_170 is Yonge-Bay
Corridor area and Hood_73 is Moss Park area in Old City of Toronto.(Toronto neighborhoods #https://www.toronto.ca/city-government/data-research-maps/neighbourhoods-communities/neighbourhood-profiles/about-toronto-neighbourhoods/)

### Suicide calls for different days and time of the day ###
The graph shows the time of the day that was most frequent for the suicide calls and day of the week that most people called for suicide PIC help. 
```{r}
#| label: fig-planes2
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)
library(patchwork)
day_colors <- c("Sunday" = "red", "Monday" = "green", "Tuesday" = "blue", "Wednesday" = "purple",
                "Thursday" = "orange", "Friday" = "brown", "Saturday" = "pink")
# Create ggplot objects for days and time

time <- cleaned_data %>%
  mutate(Time=as.POSIXct(event_hour, format="%H")) %>%
  ggplot(aes(Time, fill=fct_infreq(event_dow))) +
  geom_density(adjust=0.5, position="stack") +
  labs(x = "Hour", y = "Density", fill= "Day of Week") +
  scale_x_continuous(breaks = seq(0, 24, by = 2)) +
  scale_fill_manual(values=day_colors) +
  theme(axis.text.x=element_text(size=8)) +
  ggtitle("Frequency of Suicide Calls")

time
